The Impact of Subway Systems on Air Pollution

### 2023-02-25 output paper/Paper Two .qmd
small changes and add the bias

# 3. Example in Chile

@@

# 4. Conclusion

@@

@@

>>>>

# 3. Results: Example in Chile

@@

# 4. Discussion

@@

## 4.1 Example in China

@@

## 4.2 Bias and Limitaion

Nevertheless, there is a potential for both confounding bias and sampling bias. Confounding bias can occur when other factors, such as traffic or industrial emissions, also contribute to air pollution in subway stations. If these factors are not controlled for in a study, it may be challenging to accurately attribute air pollution levels solely to subways. Similarly, sampling bias can occur when studies only look at specific cities or types of pollution, which may not be representative of the broader population. This can lead to incomplete or inaccurate conclusions about the relationship between subways and urban air pollution. Therefore, it is essential to account for these biases for future studies and to consider a diverse range of locations and pollution types to obtain a comprehensive understanding of the topic.
